Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
please review the results section

We report our results by examining the validity of each hypothesis.

@@

@@

@@

As found in the experiments, after decreasing the amount of data resulted
in overfitting thereby confirming our hypothesis.

@@

We get unexpectedly high accuracy of 43\% even in the worst case of 1:500
imbalance in the categories while attempting to classify only the minority
categories. This is because neural networks tend to generalize well on the
most important weights.

@@

It can be interpreted from the regression that for every additional category,
we can expect the test accuracy go down by 1.88\% and test loss to go up by
6.4\% while for every additional datapoint, we can expect the accuracy to go
up by .0016\% and loss to go down by .0056\%. Both results are statistically
significant with reasonably tight confidence intervals and standard errors.

>>>>

We report our results by examining the validity of each hypothesis
related to the model and data components of performance.

@@

These results pertain to hypotheses effected by modeling choices.

@@

These results pertain to hypotheses effected by the underlying
distribution of data.

@@

As found in the experiments, after decreasing the amount of data resulted
in overfitting thereby confirming our hypothesis. Figure \ref{fig:h3Results}
contains a table with results for various number $n$ of observations.
We increased the number of categories the Neural Network had to model,
holding the number of examples per categories constant. Observations were
increased in steps of 1,000 from $n=7000$ to $n=20,000$ examples. The
number of categories $k$ ranged from $k=3$ to $k=10$ in steps of 1.

@@

Results can be seen in the Appendix with Figure \ref{fig:h4Results}. 
We get unexpectedly high accuracy of 43\% even in the worst case of 1:500
imbalance in the categories while attempting to classify only the minority
categories. This is because neural networks tend to generalize well on the
most important weights.

@@

Results for various number of classes $k$ are visualized in the Appendix
under Figure \ref{fig:h5Results}. Results for various amounts of training
data are under Figure \ref{fig:h6Results} in the Appendix. It can be
interpreted from the regression that for every additional category,
we can expect the test accuracy go down by 1.88\% and test loss to go up by
6.4\% while for every additional datapoint, we can expect the accuracy to go
up by .0016\% and loss to go down by .0056\%. Both results are statistically
significant with reasonably tight confidence intervals and standard errors.
